Combine_results

### 2017-03-10 Code/combine_results.Rmd
small change

>>>>

```{r prep_decomp_for_plotting, echo = F}
cod_decomp_results$widened_gap <- sign(cod_decomp_results$COD_cont_yrs_mean)
cod_decomp_results <- make_pretty_decomp_plot(decomp.table = cod_decomp_results, strat.var.1 = "stratum.id", 
                                   partition.bar.var = "COD", sign.var = "widened_gap",
                                   decomp.var = "COD_cont_yrs_mean", decomp.var.prop = "COD_cont_prop_mean",
                                   type.of.data = "practice")

```
